Sample-Efficient Reinforcement Learning \\ with Implicitly Quantized Representations

### 2024-02-02 paper/main.tex
moved stuff
moved another figure
Related work, fixed a reference

@@

\textbf{Reconstruction loss has a detrimental impact}
Learning to minimize the observation reconstruction error has been widely applied in model-based reinforcement learning \cite{sutton2018reinforcement, ha2018recurrent, hafnerLearning2019}, and an observation decoder has been a component of the most successful RL algorithms to date \cite{hafner2023mastering}. However, recent work \citep{zhaoSimplifiedTemporalConsistency2023,hansenTemporalDifferenceLearning2022}
has shown that incorporating a reconstruction term into the representation loss can have a negative impact on performance. They hypothesize that learning to reconstruct the observations is inefficient as they can have irrelevant details and visuals like shading that are uncontrollable by the agent and do not affect the tasks.

>>>>

\section{Related Work}
\label{sec:related_work}

@@

\textbf{Reconstruction loss has a detrimental impact}
Learning to minimize the observation reconstruction error has been widely applied in model-based reinforcement learning \cite{sutton2018reinforcement, haRecurrentWorldModels2018, hafnerLearning2019}, and an observation decoder has been a component of the most successful RL algorithms to date \cite{hafner2023mastering}. However, recent work \citep{zhaoSimplifiedTemporalConsistency2023,hansenTemporalDifferenceLearning2022}
has shown that incorporating a reconstruction term into the representation loss can have a negative impact on performance. They hypothesize that learning to reconstruct the observations is inefficient as they can have irrelevant details and visuals like shading that are uncontrollable by the agent and do not affect the tasks.
